paper1_results_figs_slimmed_50

### 2016-03-23 paper1_results_figs_slimmed_50.Rmd
added fig x8 to look at 'old' insecticide scenarios

  ## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

  ## trying with the extended experiment _ex100
  experiment <- 'extended'

@@

  # load(file=paste0(outFolder,'listOutMix_ex2_1000.rda'))
  # load(file=paste0(outFolder,'listOutI1_ex2_1000.rda'))
  # load(file=paste0(outFolder,'listOutI2_ex2_1000.rda'))

>>>>

  ## to load previously saved runs

  ## trying with the extended experiment
  experiment <- 'extended'

@@

  # load(file=paste0(outFolder,'listOutMix_unequal.rda'))
  # load(file=paste0(outFolder,'listOutI1_unequal.rda'))
  # load(file=paste0(outFolder,'listOutI2_unequal.rda'))
